---
title: "Figures for paper"
author: "Pachi Cervantes"
date: "25/03/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Figures for paper

In this section we show how to reproduce the figures contained in the paper
"A utilization distribution for the global population of Cape Vultures *Gyps coprotheres* to guide wind energy development". 
To create these figures we will need the data used for the analysis, which contains sensitive information, and therefore will 
be made available by request only.

The first two figures of the paper are not code-based and therefore we don't 
reproduce them here.


## Fig 3. Spatial distribution of tracking and colony data

```{r, eval=FALSE}

library(raster)
library(rnaturalearth)
library(sf)
library(dplyr)
library(ggplot2)

sf_use_s2(FALSE) # s2 throws an error when trying to crop


# Prepare data ------------------------------------------------------------

# Load model-ready step-selection data
ssf_data <- readRDS("data/working/data_ssf_ready_10pp.rds")

# Download South Africa map with Lesotho and Swaziland
ssa_map <- ne_countries(scale = 50, continent = "Africa", returnclass = "sf")

# Load roost and colony data
colony_orig <- read.csv("../vultRmap_data_aux/colony_data.csv")

# Transform into spatial objects
colony <- st_as_sf(colony_orig, coords = c("lon", "lat"), 
                   crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs", remove = F)


# Create grid for plotting data -------------------------------------------

# Data range
ext <- c(range(ssf_data$lon1_), range(ssf_data$lat1_))

# Add a little padding
ext <- ext + c(-5, 7.5, -1.55, 1)

# create extent
ext <- extent(ext)

# Pixel dimensions
pixsize <- 0.4

# Create raster with desired extent
omega <- raster(ext, resolution = rep(pixsize, 2), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

# Crop Africa map
ssa_map_cp <- st_crop(ssa_map, y = ext)


# Plot distribution of tracking locations ---------------------------------

# Count observations per pixel (only data not pseudo-absences)
counts <- ssf_data %>% 
    filter(case_ == TRUE) %>% 
    dplyr::select(lon1_, lat1_) %>% 
    rasterize(omega, fun='count', background = 0)

counts_df <- as.data.frame(counts, xy = T) %>% 
  rename(count = layer) %>% 
  mutate(count = if_else(count == 0, NA_real_, count),
         log_count = log(count))

ggplot() +
  geom_sf(data = ssa_map_cp) +
  geom_raster(data = counts_df, aes(x = x, y = y, fill = log_count)) +
  geom_sf(data = ssa_map_cp, fill = NA) +
  scale_fill_viridis_c(na.value = "transparent", option = "A", direction = -1,
                       name = "log \n count") +
  theme_void() +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))


# Plot distribution of colony locations -----------------------------------

# Count points per pixel
colsize <- colony %>% 
   mutate(total = avg_ad + avg_juv) %>% 
   as("Spatial") %>% 
   rasterize(y = omega, field = "total", fun='sum', background = 0)


# Plot distribution of tracking locations
counts_df <- as.data.frame(colsize, xy = T) %>% 
   rename(size = layer) %>% 
   mutate(size = if_else(size == 0, NA_real_, size),
          log_size = log(size))

ggplot() +
   geom_sf(data = ssa_map_cp) +
   geom_raster(data = counts_df, aes(x = x, y = y, fill = log_size)) +
   geom_sf(data = ssa_map_cp, fill = NA) +
   scale_fill_viridis_c(na.value = "transparent", option = "D", direction = -1,
                      name = "log \n size") +
   theme_void() +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

```


## Fig 4. Cross-validation results

```{r, eval=FALSE}

library(dplyr)
library(ggplot2)

mytheme <- theme_bw() +
   theme(panel.grid = element_blank(),
         text = element_text(size = 15),
         legend.text = element_text(size = 15),
         legend.title = element_text(size = 15),
         axis.text = element_text(size = 15),
         plot.title = element_text(size = 15))


# Cross-validation for step selection ------------------------------------

# Directory where the cross-validation results are
resultsdir <- "output/cv_results/ssf_cv/"

# Load files
files <- list.files(resultsdir, pattern = "cv_results_[1-9]t[1-2].rds")

cv_results <- data.frame()

for(i in seq_along(files)){
   cv_results <- rbind(cv_results,
                       readRDS(paste0(resultsdir, files[i])))
}

# For some groups we ran more than 10 rounds so we must subset the
# first 10 to compare the same amount for all groups
cv_results %>% 
   group_by(mod) %>% 
   slice(1:10) %>% 
   summarize(mean = mean(cv_pi, na.rm = TRUE),
             sd = sd(cv_pi, na.rm = TRUE),
             n = n())

cv_results %>% 
   group_by(mod) %>% 
   slice(1:10) %>% 
   ungroup() %>% 
   ggplot() +
   geom_boxplot(aes(x = factor(mod), y = cv_pi)) +
   geom_jitter(aes(x = factor(mod), y = cv_pi),
               colour = "red", alpha = 0.5, width = 0.1) +
   xlab("") + ylab("Spearman Rank Correlation") +
   mytheme


# Cross-validation for risk height ------------------------------------

# Directory where the cross-validation results are
resultsdir <- "output/cv_results/hgt_cv/"

# Load files
files <- list.files(resultsdir, pattern = "cv_results_height_[1-6].rds")

cv_results <- data.frame()

for(i in seq_along(files)){
   cv_results <- rbind(cv_results,
                       readRDS(paste0(resultsdir, files[i])))
}

cv_results %>% 
   group_by(mod) %>% 
   summarize(mean = mean(cv_auc, na.rm = TRUE),
             sd = sd(cv_auc, na.rm = TRUE),
             n = n())

cv_results %>% 
   ggplot() +
   geom_boxplot(aes(x = factor(mod), y = cv_auc)) +
   geom_jitter(aes(x = factor(mod), y = cv_auc),
               colour = "red", alpha = 0.5, width = 0.1) +
   xlab("") + ylab("AUC") +
   mytheme


```


## Fig 5. Covariate effects plots

```{r, eval=FALSE}

library(dplyr)
library(ggplot2)
library(glmmTMB)
library(khroma)

mytheme <- theme_bw() +
   theme(panel.grid = element_blank(),
         text = element_text(size = 15),
         legend.text = element_text(size = 15),
         legend.title = element_text(size = 15),
         axis.text = element_text(size = 15),
         plot.title = element_text(size = 15))

# Effects in step-selection -------------------------------------------

# Model fit
ssf_fit <- readRDS("../vultRmap_data_aux/ssf_fit_10pp.rds")
ssf_fit_summ <- summary(ssf_fit)

# Extract effects
fit_effects <- ssf_fit_summ$coefficients$cond %>% 
   as.data.frame() %>% 
   mutate(name = rownames(.)) %>% 
   rename_all(make.names) %>% 
   rename_all(tolower)

# Fix names
names(fit_effects) <- str_replace_all(names(fit_effects), "\\.\\.", "\\.")
names(fit_effects) <- str_replace_all(names(fit_effects), "\\.\\.", "\\.")
names(fit_effects)

# Adult effects
ad_effects <- fit_effects %>% 
   filter(!str_detect(name, "juv"))

# Juvenile effects
juv_effects <- fit_effects %>% 
   filter(str_detect(name, "juv")) %>% 
   mutate(name2 = str_remove(name, ":juv"))

juv_effects <- ad_effects %>% 
   left_join(juv_effects, by = c("name" = "name2")) %>% 
   mutate(estimate.y = if_else(is.na(estimate.y), 0, estimate.y),
          std.error.y = if_else(is.na(std.error.y), 0, std.error.y),
          estimate = estimate.x + estimate.y,
          std.error = sqrt(std.error.x^2 + std.error.y^2)) %>% 
   dplyr::select(name, estimate, std.error)

# All effects
all_effects <- ad_effects %>% 
   dplyr::select(name, estimate, std.error) %>% 
   mutate(age = "ad") %>% 
   rbind(juv_effects %>% 
            dplyr::select(name, estimate, std.error) %>% 
            mutate(age = "juv"))

# Random effect variances
rdm_sd <- ssf_fit_summ$varcor

rdm_sd <- map_dbl(rdm_sd$cond, ~sqrt(.x))

namesrdm <- map_chr(ssf_fit_summ$varcor$cond, ~rownames(.x))

rdm_eff <- data.frame(name = namesrdm,
                      sd = rdm_sd)


all_effects <- all_effects %>% 
   left_join(rdm_eff, by = "name")

all_effects %>% 
   mutate(var_fct = factor(name, levels = arrange(ad_effects, estimate) %>% pull(name))) %>% 
   ggplot()+
   geom_linerange(aes(xmin = estimate-1.96*std.error, xmax = estimate+1.96*std.error, y = var_fct, col = age),
                  position = position_dodge(width = 0.5), lwd = 1.5) +
   geom_pointrange(aes(x = estimate, xmin = estimate-sd, xmax = estimate+sd, y = var_fct, col = age),
                   position = position_dodge(width = 0.5)) +
   geom_vline(aes(xintercept = 0), linetype = 2) +
   scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
   scale_colour_highcontrast(name = "Age") +
   xlab("") + ylab("") +
   mytheme


# Effects on risk height -------------------------------------------

# Load risk height model fit
hgt_fit <- readRDS("../vultRmap_data_aux/height_fit.rds")
hgt_fit_summ <- summary(hgt_fit)

# Extract effects
fit_effects <- hgt_fit_summ$coefficients$cond %>% 
   as.data.frame() %>% 
   mutate(name = rownames(.)) %>% 
   rename_all(make.names) %>% 
   rename_all(tolower)

# Fix names
names(fit_effects) <- str_replace_all(names(fit_effects), "\\.\\.", "\\.")
names(fit_effects) <- str_replace_all(names(fit_effects), "\\.\\.", "\\.")
names(fit_effects)

# Random effect variances
rdm_sd <- hgt_fit_summ$varcor

rdm_sd <- map_dbl(rdm_sd$cond, ~sqrt(.x))

namesrdm <- map_chr(hgt_fit_summ$varcor$cond, ~rownames(.x))

rdm_eff <- data.frame(name = namesrdm,
                      sd = rdm_sd)

fit_effects <- fit_effects %>% 
   left_join(rdm_eff, by = "name")

fit_effects %>% 
   mutate(var_fct = factor(name, levels = arrange(fit_effects, estimate) %>% pull(name))) %>% 
   ggplot()+
   geom_linerange(aes(xmin = estimate-1.96*std.error, xmax = estimate+1.96*std.error, y = var_fct),
                  position = position_dodge(width = 0.5), lwd = 1.5) +
   geom_pointrange(aes(x = estimate, xmin = estimate-sd, xmax = estimate+sd, y = var_fct),
                   position = position_dodge(width = 0.5)) +
   geom_vline(aes(xintercept = 0), linetype = 2) +
   scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
   xlab("") + ylab("") +
   mytheme

```

## Fig 6. Utilization distribution and population utilization distribution in 2D

```{r,eval=FALSE}
library(dplyr)
library(sf)
library(raster)
library(vultRmap)

# Prepare buffer around EC colonies ---------------------------------------

# Load colony data
colony_all <- read.csv("../vultRmap_data_aux/colony_data.csv")

# Filter those colonies we are interested in
col_sel <- colony_all %>%
   dplyr::filter(id %in% c("da_32", "da_65", "da_201", "da_75", "da_24",
                           "da_9", "da_200", "da_38", "da_27", "da_239",
                           "da_4", "cvcol669", "cvco719", "cvcol687", "cvcol589")) %>%
   st_as_sf(coords = c("lon", "lat"), crs = 4326)

# Create a 50 kilometer buffer
sf_use_s2(FALSE)
col_sel_buff <- col_sel %>%
   st_combine() %>%
   st_convex_hull() %>%
   st_sf() %>%
   st_buffer(dist = 0.4)

col_sel_buff <- col_sel_buff %>%
   st_union() %>%
   st_sf()


# Plot hazard and risk maps -----------------------------------------------

# Set directory where .tif maps are stored
mapdir <- "../vultRmap_data_aux/risk_maps/"

# Define maps to plot and save
maps <- paste0(c("hazard_", "risk_"), "total")

# For raster reclassification
nlevels <- 10
udlevels <- seq(0, 1, length.out = nlevels + 1)

# Reclassify and trim all maps
rr <- vector("list", length = length(maps))

for(i in seq_along(maps)){
   
   # Reclassify
   r <- raster::raster(paste0(mapdir, maps[i], ".tif"))
   
   # Remove 0.1% of activity to reduce mapping and reclassify
   rcl_map <- vultRmap::makeBinnedRasterMap(r, nlevels = 10, cutoff = 0.99)
   
   # Crop map to remove outer NAs
   frame <- extent(c(12, 40, -37, -17))
   rcl_map <- crop(rcl_map, frame)
   
   # Save raster
   rr[[i]] <- rcl_map
   
}
   
# Set all maps to the same extent
exts <- lapply(rr, extent)
 
f <- function(r, exts){
   for(i in seq_along(exts)){
      r <- extend(r, exts[[i]])
   }
   return(r)
}
   
rr <- lapply(rr, f, exts)   

# Crop ssa_map
ssa_map <- st_crop(ssa_map, extent(rr[[1]]))

# Plot
rr <- stack(rr)
names(rr) <- c("UD_2D","PUD_2D")
rr <- as.data.frame(rr, xy = TRUE)

# 2D maps
rr %>% 
    dplyr::select(x, y, UD_2D, PUD_2D) %>% 
    tidyr::pivot_longer(cols = -c("x", "y"), names_to = "map") %>% 
    mutate(map = factor(map, levels = unique(map), 
                        labels = paste("2-D", c("utilization", "population"), "distribution"))) %>% 
    ggplot() +
    geom_raster(aes(x = x, y = y, fill = value)) +
    geom_sf(data = col_sel_buff, fill = "grey", linetype = "solid", alpha = 0.3) +
    geom_sf(data = ssa_map, fill = NA, size = 0.05) +
    scale_fill_viridis_c(name = "", option = "inferno", direction = 1, na.value = NA) +
    facet_wrap("map") +
    xlab("") + ylab("") +
    theme_bw() +
    theme(axis.text = element_text(size = 8),
          legend.text = element_text(size = 10),
          strip.text = element_text(size = 10))


```


## Fig 7 and Fig 8. SABAP2 vs population utilization distribution

```{r, eval=FALSE}

library(ABAP) # To install ABAP remotes::install_github("AfricaBirdData/ABAP")
library(dplyr)
library(tidyr)
library(ggplot2)
library(sf)
library(raster)
library(vultRmap)

rm(list = ls())

ABAP::searchAbapSpecies("vulture")

cv_sabap_sa <- getAbapData(.spp_code = 106, .region_type = "country",
                         .region = "South Africa")

cv_sabap_sa %>% 
   mutate(year = lubridate::year(StartDate)) %>% 
   pull(year) %>% 
   unique()

cvRepRate <- function(region){
   
   cv_sabap <- getAbapData(.spp_code = 106, .region_type = "country",
                            .region = region)
   
   pentads <- ABAP::getRegionPentads(.region_type = "country",
                                     .region = region)
   
   # Calculate reporting rate
   reprate <- cv_sabap %>% 
      mutate(year = lubridate::year(StartDate)) %>% 
      filter(year > 2007, year < 2021) %>% 
      group_by(Pentad, Spp) %>% 
      summarise(n = n()) %>% 
      ungroup() %>% 
      rename(detc = Spp) %>% 
      mutate(detc = if_else(detc == "-", 0L, 1L)) %>% 
      complete(Pentad, nesting(detc = c(0L, 1L)), fill = list(n = 0)) %>% 
      arrange(Pentad, detc) %>% 
      pivot_wider(names_from = detc, names_prefix = "det", values_from = n) %>% 
      mutate(effort = det1 + det0,
             rep_rate = det1 / effort)
   
   pentads_cv <- pentads %>% 
      left_join(reprate, by = c("Name" = "Pentad")) %>% 
      filter(!is.na(rep_rate))
   
   return(pentads_cv)
}


# South Africa ------------------------------------------------------------

SA <- cvRepRate("South Africa")
LST <- cvRepRate("Lesotho")
SWZ <- cvRepRate("Eswatini")

pentads_cv <- rbind(SA, LST, SWZ)

plot(pentads_cv["rep_rate"], lwd = 0.1)

# Subset those pentads that have 5 or more cards
pentads_cv <- pentads_cv %>% 
   filter(effort > 4)

# Load PUD map
risk <- raster("../vultRmap_data_aux/risk_maps/risk_total.tif")

# Reclassify raster into cumulative PUD
rcl_risk <- vultRmap::makeBinnedRasterMap(risk, nlevels = 100, cutoff = 1)

# Crop map
frame <- extent(c(15, 40, -37, -17))
rcl_risk <- crop(rcl_risk, frame)

# Extract risk values
pentads_risk <- exactextractr::exact_extract(rcl_risk, st_zm(pentads_cv), "mean")

pentads_cv$risk <- exactextractr::exact_extract(risk, st_zm(pentads_cv), "mean")

pentads_cv$cum_risk <- pentads_risk


# Plots -------------------------------------------------------------------

# Load SA background (download South Africa map with Lesotho and Swaziland)
ssa_map <- rnaturalearth::ne_countries(scale = 50, continent = "Africa", returnclass = "sf") %>% 
   filter(admin %in% c("South Africa", "Lesotho", "Swaziland") )

ssa_map <- ssa_map %>% 
   st_crop(pentads_cv)

# Plot SABAP vs. cumPUD
legend_names <- c(expression("cumPUD"), "RepRate")

pp <- pentads_cv %>% 
    mutate(pd = risk,
           log_pd = log(pd+0.1)) %>% 
    dplyr::select(Name, rep_rate, cum_risk) %>% 
    tidyr::pivot_longer(cols = -c(Name, geometry),
                        names_to = "param",
                        values_to = "value") %>% 
    group_split(param) %>% 
    map2(., legend_names, ~ggplot(data = .x) +
             geom_sf(data = ssa_map, fill = "grey") +
             geom_sf(aes(fill = value), size = NA) +
             scale_fill_viridis_c(name = .y, option = "C", direction = 1) +
             theme_classic() +
             theme(axis.text = element_blank(),
                   axis.ticks = element_blank(),
                   axis.title = element_blank(),
                   axis.line = element_blank())#,
         # legend.position = "none")
    )

comp_pud <- pentads_cv %>% 
    mutate(pd = risk,
           log_pd = log(pd+0.1)) %>% 
    dplyr::select(Name, rep_rate, cum_risk) %>% 
    ggplot() +
    geom_sf(data = ssa_map, fill = "grey") +
    geom_sf(aes(fill = cum_risk), size = NA) +
    scale_fill_viridis_c(name = legend_names[1], option = "C", direction = -1) +
    theme_classic() +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          axis.line = element_blank())

comp_rr <- pentads_cv %>% 
    mutate(pd = risk,
           log_pd = log(pd+0.1)) %>% 
    dplyr::select(Name, rep_rate, cum_risk) %>% 
    ggplot() +
    geom_sf(data = ssa_map, fill = "grey") +
    geom_sf(aes(fill = rep_rate), size = NA) +
    scale_fill_viridis_c(name = legend_names[2], option = "C", direction = 1) +
    theme_classic() +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          axis.line = element_blank())

gridExtra::grid.arrange(comp_pud, comp_rr, ncol = 2)


# Fit binomial model ------------------------------------------------------

lm1 <- glm(rep_rate ~ cum_risk, family = "binomial", weights = effort,
           data = pentads_cv)

summary(lm1)

# Predict for data
est <- predict(lm1, se.fit = TRUE, type = "link")


invLogit <- function(x){
    exp(x) / (1 + exp(x))
}

# Add prediction interval
source("R/functions/simulateBinomPI.R")

newdata <- data.frame(cum_risk = seq(min(pentads_cv$cum_risk, na.rm = T), 1, length.out = 1000),
                      rep_rate = runif(1000, 0, 1),
                      effort = 100,
                      weights = 100)

preds <- simulateBinomPi(df = newdata,
                         fit = lm1,
                         names = c("lpb", "upb"),
                         alpha = 0.1,
                         nSims = 1000)

preds %>%
    ggplot() +
    geom_point(data = pentads_cv, aes(x = cum_risk, y = rep_rate), alpha = 0.5) +
    geom_line(aes(x = cum_risk, y = pred), col = "red", size = 1) +
    geom_ribbon(aes(x = cum_risk, ymin = lpb, ymax = upb), col = "grey", alpha = 0.3) +
    ylab("SABAP2 reporting rate") + xlab("cumPUD") +
    theme_classic() +
    theme(axis.text = element_text(size = 10),
          axis.title = element_text(size = 12))


```


## Fig 9. Analysis of REDZs Cape Vulture encounter risk

```{r, eval=FALSE}

library(tidyverse)
library(raster)
library(sf)
library(vultRmap)

rm(list = ls())


# Define regions --------------------------------------------------

# Download country borders. This might take a while
SA <- raster::getData("GADM", country="South Africa", level=1, path = tempdir())
LTS <- raster::getData("GADM", country="Lesotho", level=1, path = tempdir())
SWZ <- raster::getData("GADM", country="Swaziland", level=1, path = tempdir())
BWA <- raster::getData("GADM", country="Botswana", level=1, path = tempdir())
NAM <- raster::getData("GADM", country="Namibia", level=1, path = tempdir())
ZWE <- raster::getData("GADM", country="Zimbabwe", level=1, path = tempdir())
MOZ <- raster::getData("GADM", country="Mozambique", level=1, path = tempdir())

# For Lesotho and Swaziland we will predict for the whole countries rather than
# provinces
LST$NAME_1 <- LST$NAME_0
SWZ$NAME_1 <- SWZ$NAME_0
BWA$NAME_1 <- BWA$NAME_0
NAM$NAME_1 <- NAM$NAME_0
ZWE$NAME_1 <- ZWE$NAME_0
MOZ$NAME_1 <- MOZ$NAME_0

# South Africa gets plotted with Lesotho and Swaziland
SA_total <- rbind(SA,LST,SWZ) %>%
      st_as_sf() %>%
      dplyr::select(NAME_1)

SA_total <- SA_total %>%
      group_by(NAME_1) %>%
      summarise(m = unique(NAME_1)) %>%
      st_cast()

range_total <- rbind(SA,LST,SWZ, BWA, NAM, ZWE, MOZ) %>%
      st_as_sf() %>%
      dplyr::select(NAME_1)


# Load data ---------------------------------------------------------------

# Load PUD raster
risk <- raster("../vultRmap_data_aux/risk_maps/pud_total.tif")

# Load REDZ. These can be downloaded from https://egis.environment.gov.za/redz
redz1 <- st_read("data/working/Phase1_REDZs/REDZs.shp")
redz2 <- st_read("data/working/Phase2_REDZs/PHASE 2_REDZs.shp")

# Get both shapes in the same coordinate system and combine
redz1 <- st_transform(redz1, st_crs(redz2))

redz <- rbind(dplyr::select(redz1, Name),
              dplyr::select(redz2, Name))


# Extract PUD per province

# Extract provincial risk
prov_risk <- calcRegionRisk(range_total, ref_area = NULL, ud_map = risk)


# Extract PUD risk per REDZ

# Extract risk values for each REDZ using total range as reference
redz_national <- calcRegionRisk(region = redz, ref_area = range_total, ud_map = risk)


# Order redz by increasing avg PUD
lvs <- redz_national %>%
   arrange(desc(pud_avg)) %>%
   pull(Name) %>%
   unique()

redz_national <- redz_national %>%
   mutate(Name = factor(Name, levels = lvs))

# Analyse risk taking province as a reference
redz <- redz %>%
   mutate(province = case_when(Name == "Stormberg Wind" ~ "Eastern Cape",
                               Name == "Overberg Wind" ~ "Western Cape",
                               Name == "Emalahleni" ~ "Mpumalanga",
                               Name == "Beaufort West" ~ "Western Cape",
                               Name == "Klerksdorp" ~ "North West",
                               Name == "Cookhouse Wind" ~ "Eastern Cape",
                               Name == "Vryburg Solar" ~ "North West",
                               Name == "Kimberley Solar" ~ "Free State",
                               Name == "Komsberg Wind" ~ "Western Cape",
                               Name == "Springbok Wind" ~ "Northern Cape",
                               Name == "Upington Solar" ~ "Northern Cape"))

redz_prov <- vector("list", nrow(redz))

for(i in seq_along(redz_prov)){
   prov <- filter(SA_total, NAME_1 == redz$province[i])
   redz_prov[[i]] <- calcRegionRisk(region = redz[i,], ref_area = prov, ud_map = risk)
}

redz_prov <- do.call("rbind", redz_prov)

redz_prov <- redz_prov %>%
   st_drop_geometry() %>%
   rename(prop_prov = pud_prop) %>%
   left_join(redz_national %>%
                st_drop_geometry() %>%
                dplyr::select(Name, pud_prop),
             by = "Name") %>%
   rename(prop_nat = pud_prop)



# Plot REDZ risk ----------------------------------------------------------

# Relate risk to REDZs
redz_risk <- exactextractr::exact_extract(risk, redz)
redz_risk <- map2_dfr(redz_national$Name, redz_risk, ~tibble(name = .x, risk = .y$value))

risk_UD <- makeBinnedRasterMap(risk, nlevels = 10, cutoff = 0.99)

# Clip to South Africa for plotting
risk_df <- as.data.frame(crop(risk_UD, SA_total), xy = TRUE)

redz_bars <- redz_national %>%
   ggplot() +
   geom_pointrange(aes(x = pud_avg,
                       xmin = pmax(0, pud_avg - pud_sd),
                       xmax = pud_avg + pud_sd,
                       y = Name, colour = Name), fatten = 0.5, size = 0.5) +
   scale_y_discrete(limits=rev) +
   scale_colour_viridis_d(option = "D", direction = 1) +
   ylab("") + xlab("PUD") +
   theme_bw() +
   theme(axis.text = element_text(size = 10),
         axis.text.y = element_blank(),
         axis.title = element_text(size = 10),
         legend.position = "none")

redz_violplot <- redz_risk %>%
      ggplot() +
      geom_violin(aes(x = log(risk), y = name, fill = name)) +
      scale_y_discrete(limits=rev) +
      scale_fill_viridis_d(option = "D", direction = 1) +
      ylab("") + xlab("log(PUD)") +
      theme_bw() +
      theme(axis.text = element_text(size = 10),
            axis.title = element_text(size = 10),
            legend.position = "none")

# Fix REDZ's names to include a number
redz_national <- redz_national %>% 
    arrange(desc(pud_avg)) %>% 
    mutate(Name = paste(row_number(), Name, sep = ".")) %>%
    mutate(Name = factor(Name, levels = Name))

sf::sf_use_s2(FALSE)
redz_number <- st_centroid(redz_national) %>% 
    mutate(lab = row_number())

redz_riskmap <- ggplot() +
    geom_raster(data = risk_df, aes(x = x, y = y, fill = layer),
                alpha = 1, show.legend = FALSE) +
    geom_sf(data = SA_total, fill = NA, linetype = 2, size = 0.3) +
    geom_sf(data = redz_national, aes(colour = Name), fill = NA) +
    geom_sf_text(data = redz_number, aes(label = lab), size = 3, fontface = "bold") +
    # scale_fill_gradient(low = "white", high = "#CC089B") +
    scale_fill_viridis_c(option = "inferno", direction = 1, na.value = NA) +
    scale_colour_viridis_d(option = "D", direction = 1, name = "") +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_classic() +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          axis.line = element_blank(),
          legend.text = element_text(size = 10),
          panel.border = element_rect(fill = NA))

gridExtra::grid.arrange(redz_violplot, redz_bars, redz_riskmap,
                        nrow = 5, ncol = 3,
                        layout_matrix = cbind(c(1,1,3,3,3),
                                              c(1,1,3,3,3),
                                              c(1,1,3,3,3),
                                              c(2,2,3,3,3),
                                              c(2,2,3,3,3)))




```

