---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# A utilization distribution for the population of Cape Vultures

<!-- badges: start -->
<!-- badges: end -->

This repository contains the code used in the paper "A utilization distribution for the global population of Cape Vultures *Gyps coprotheres* to guide wind energy development", *Ecological Applications* 2023. Here you will find all the scripts used for processing the data and run the models that are used for building the utilization distribution for the population of Cape Vultures. There is a second repo that is used to produce a map by simulating vulture activity from the fitted models. The simulation routines were separated from the fitting routines and packed into a package to be able to easily update the maps, when more/better information becomes available. Throughout the publication process, we used different terminology to refer to the same things. We started thinking of utilizaton distribution as being indicative of 'risk' and therefore you might find references to risk throughout.

Some of the processing and fitting scripts take quite long to run. Therefore, run only if completely necessary and go find something to do. In addition, some of the scripts are better suited to run in a high performance computing environment (HPC), because the are very demanding of RAM memory. These will be flagged throughout the document, to proceed with care.

Note, paths to specific directories where data or outputs are hosted, need to be adapted to the user configuration.

## Pre-processing of tracking and colony data

```{r, eval=FALSE}

library(tidyverse)

# Load processing scripts directories
scripts <- dir("R/1_data_processing")

# Remove those used for the creation of templates.
# If you want to overwrite templates you will have to run those scripts directly
# (see data_processing/0_create_templates)
scripts <- scripts[str_detect(scripts, "0", negate = T)]

```


### Run processing scripts for specific birds

The objective of the data processing scripts is to bring all bird-tracking files
to a common standard. Different types of tags have their own characteristics, and
therefore, scripts are slightly different for different birds.

```{r, eval=FALSE}

proc <- scripts[1:18]

for(f in 1:length(proc)){
  
  # Need to reload scripts because of the rm() calls inside the scripts
  scripts <- dir("R/1_data_processing")
  scripts <- scripts[str_detect(scripts, "0", negate = T)]
  proc <- scripts[1:18]
  
  print(f)
  
  source(paste0("R/1_data_processing/", proc[f]))
  
}

# Also run fine processing: exclude certain birds, cut out certain periods, change ages for
# long term tracking, re-sample very high resolution tracks. Do before any colony processing
source("R/1_data_processing/3_fine_process.R")

```


### Prepare colony data

The colony data-processing scripts are used for bringing together colony data from
different sources and format them to a common standard. This entails finding
colonies that are repeated in the different sources to elaborate a unique list,
and calculate the average size of the colonies.

```{r, eval=FALSE}

# Load scripts
scripts <- dir("R/2_colony_processing")

# Run the processing scripts for colonies
for(s in seq_along(scripts)){
  
  print(s)
  
  # # Need to reload scripts because of the rm() calls inside the scripts
  scripts <- dir("R/2_colony_processing")
  source(paste0("R/2_colony_processing/", scripts[s]))
}

```

Once the colony data-processing scripts have been run, we can determine what
colonies each of the tracked vultures are using each year.

```{r, eval=FALSE}

# Run the colony process scripts in which we find the central places of the 
# vultures (WE SHOULD HAVE RAN "R/2_colony_finding/5_colony_finding.R" ALREADY)
source("R/1_data_processing/4_colony_process.R")

```


### Find movement modes

For some of the analysis we are interested in those tracking fixes that correspond
to moving birds. To separate movement from resting modes, we used either
Hidden Markov Models or finite mixture models. Running these models for all birds
takes really long, so consider running in an HPC. If ran in an HPC, there is a
second part in the script (from "Explore state proportions") that must be ran in
the local script if one wants to explore state proportions and things like that.
Do it manually.

```{r, eval=FALSE}
source("R/1_data_processing/5_move_mode_process.R")
```


### Prepare raster covariates

In this scripts we will prepare the covariates used for fitting the step-selection
and collision height model.

```{r, eval=FALSE}

# Create slope and ruggedness rasters from elevation. Also set sea level = 0
# Takes a while
source("R/3_prepare_covts/1_prep_covts_topo_rasters.R")

# Re-classify habitats and create a csv file with the codes
source("R/3_prepare_covts/2_prep_land_cover.R")

# Create a single shapefile with protected areas
source("R/3_prepare_covts/3_prep_prot_areas.R")

# Identify steep slopes to calculate distance to them later
# Might have to unload certain packages for it to run properly (best just re-start R)
# This variable did not go into the final model, it is only used for alternative
# models
source("R/3_prepare_covts/4_prep_steep_slopes.R")

# Create rasters with distance to steep slopes to use as covariates
# This takes very long, so don't run unless completely necessary.
# This variable did not go into the final model, it is only used for alternative
# models
source("R/3_prepare_covts/5_prep_dist_slp.R")

# Increase the resolution of distance to slopes and transform to meters.
# This variable did not go into the final model, it is only used for alternative
# models
source("R/3_prepare_covts/5a_red_dist_slp_m.R")

# Prepare the supplementary feeding sites file for processing
source("R/3_prepare_covts/6_prep_covts_restaurants.R")

```


### Run additional tracking data height processing scripts

Some tracking tags had heights wrap down to zero when they went above 2042. To
correct this and other issues producing nonsensical outliers we run the following
script. There will be some final processing in another script right before fitting

```{r, eval=FALSE}
source("R/1_data_processing/6_height_process.R")

```

Additionally, we run another script to detect anomalies in the distance travelled
by the birds. Some of the individuals analysed were rehabilitated birds that
might not exhibit a representative behaviour of the species in general.

```{r, eval=FALSE}

# Analyze distance traveled per day to try to detect anomalies
source("R/1_data_processing/7_dist_process.R")

```


### Create a database and prepare model-fitting data

```{r, eval=FALSE}

# Create a database with the new information extracted from the birds
source("R/1_data_processing/8_create_db_fit_ready.R")

```

Prepare data for fitting step-selection models.

```{r, eval=FALSE}

# Regularize trajectories, create pseudo-absences and annotating with covariates
# We tested different number of pseudo-absence points. For the final model we
# used 10 but for model selection, to save time and memory we used 5pp
source("R/4_ssf_model/1c_prep_ssf_data_10pp.R")

```

Prepare data for fitting collision height model

```{r, eval=FALSE}

# Annotating with covariates
source("R/5_height_model/1_prep_height_data.R")

# Final run of processing to fix some height records
source("R/5_height_model/1b_height_data_fix.R")

```


## Model fitting

We used cross-validation routines for model selection. These routines are memory
demanding and take long to run, because models need to fitted multiple times. It
is highly recommended to run these scripts in a high performance computing environment.

```{r, eval=FALSE}

# Run cross-validation for step-selection models
source("R/4_ssf_model/2_cv_hier_ssf.R")

# Fit best model
source("R/4_ssf_model/3_fit_hier_ssf.R")

```


```{r, eval=FALSE}

# Run cross-validation for collision height models
source("R/5_height_model/2_cv_hier_height.R")

# Fit best model
source("R/5_height_model/3_fit_hier_bern_height.R")

```


## Predicting utilization distributions

Cape Vulture simulation of activity is performed from the [vultRmap](https://github.com/patchcervan/vultRmap)
repository. There, we find the routines for predicting habitat preferences of the
species over new environments, simulate activity using these preferences and movement
constraints identified by the step-selection model, and finally produce utilization
distribution maps. Please, refer to that repository for how simulation and mapping is done.
